Learning filters from user provided image makers for convolutional neural networks

### 2020-06-08 main.tex
Updates from Overleaf
update SVM results

\usepackage[pdftex]{graphicx}
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
\usepackage{comment}
\usepackage{float}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{bm}

@@

@@

@@

\begin{table}[!t]
  \begin{center}
  \begin{tabular}{|l|c|c|c|}
  \hline
   Method & Precision & Recall & F-score \\
  \hline\hline
    I-Ours & $\boldsymbol{0.86 \pm 0.01}$ & $\boldsymbol{0.84 \pm 0.02}$ & $\boldsymbol{0.85 \pm 0.02}$\\
    II-Ours (fine tuned) & $\boldsymbol{0.86 \pm 0.01}$ & $\boldsymbol{0.84 \pm 0.02}$ & $0.84 \pm 0.02$\\
    III-Ours with SVM & $0.81 \pm 0.02$ & $0.77 \pm 0.03$ & $0.78 \pm 0.02$\\
    IV-VGG & $0.84 \pm 0.01$ & $0.76 \pm 0.03$ & $0.77 \pm 0.02 $ \\
    V-VGG (fine tuned) & $0.84 \pm 0.01$ & $0.75 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  \hline
  \end{tabular}
  \end{center}
  \caption{Results.}
  \label{tab:results}
\end{table}

@@

Our method achieved better precision than conventionally trained VGG, and the difference between precision and recall is much smaller. The Linear SVM did not prove to be a good classifier like the MLP, but, on average, it still got a little better than the VGG-16. Using our method as initialization and training the entire network with backpropagation did not improve the result; this implies that the filters we created are already good filters given the training set. Our feature extractor training method was able to learn good filters from a minimal set of images. VGG has many parameters to learn, so it is susceptible to overfitting with such a small training set. We do not use any technique to handle small data sets to train VGG because we intended to verify our approach viability, and these techniques could also be used with our method. In Figure \ref{fig:ex-classification} we can see examples of misclassified images. In these images, coconut trees appear in different angles, sizes, and shapes, or the boundaries between the coconut tree and the background are tenuous, making it more difficult to identify them. In turn, images that do not contain coconut trees, contain trees that resemble their shape.

>>>>

\usepackage[pdftex]{graphicx}
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
\usepackage{comment}
\usepackage{float}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{calc}

@@

\definecolor{navy}{RGB}{0,0,137}
\definecolor{tealDeer}{RGB}{148,232,180}
\definecolor{dodgerBlue}{RGB}{18,161,255}
\definecolor{citrine}{RGB}{230, 194, 8}
\definecolor{violet}{RGB}{112,5,164}
\definecolor{navyPurple}{RGB}{172,86,253}
\definecolor{heliotrope}{RGB}{236,93,253}

@@

\begin{figure}
  \begin{center}
  \tikzset{
    treenode/.style = {shape=rectangle, rounded corners,
                       draw=black, align=center, line width=width},
    specialedge/.style = {line width=1.5pt}
  }

  \begin{tikzpicture}
    [
      grow                    = down,
      sibling distance        = 5em,
      level distance          = 3em,
      edge from parent/.style = {draw=black},
      every node/.style       = {treenode},
      sloped
    ]
    \node [treenode, fill=tealDeer, label = {[label distance = 0.5em]}] (v0) {Conv$(60 \times 7 \times 7)$}
      child {
        child {
          child {
                child {
                  node [treenode, fill=navyPurple] {Classifier}
                  edge from parent
                }
                node [treenode, fill=tealDeer] {BatchNorm}
                edge from parent
           }
          node [treenode, fill=tealDeer] {MaxPool$(3\times3)$}
          edge from parent
        }
        node [treenode, fill=dodgerBlue, label = {[label distance = 0.5em] }] {ReLU} 
        edge from parent
      };

  \end{tikzpicture}

  \end{center}
  \caption[An output example of the algorithm to compute a core stable coalition structure.]{An output example of the algorithm to compute a core stable coalition structure for games represented by forests. Each color represents a coalition.}
  \label{fig:tree}
\end{figure}

@@

\begin{table}[!t]
  \begin{center}
  \begin{tabular}{|l|c|c|c|}
  \hline
   Method & Precision & Recall & F-score \\
  \hline\hline
    I-Ours & $\boldsymbol{0.86 \pm 0.01}$ & $\boldsymbol{0.84 \pm 0.02}$ & $\boldsymbol{0.85 \pm 0.02}$\\
    II-Ours (fine tuned) & $\boldsymbol{0.86 \pm 0.01}$ & $\boldsymbol{0.84 \pm 0.02}$ & $0.84 \pm 0.02$\\
    III-Ours with SVM & $0.836 \pm 0.015 $ & $ 0.793 \pm 0.025$ & $ 0.804 \pm 0.022$\\
    IV-VGG & $0.84 \pm 0.01$ & $0.76 \pm 0.03$ & $0.77 \pm 0.02 $ \\
    V-VGG (fine tuned) & $0.84 \pm 0.01$ & $0.75 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  \hline
  \end{tabular}
  \end{center}
  \caption{Results.}
  \label{tab:results}
\end{table}

@@

Our method achieved better precision than conventionally trained VGG, and the difference between precision and recall is much smaller. The Linear SVM did not prove to be a good classifier like the MLP, but, on average, it still got a little better than the VGG-16. Using our method as initialization and training the entire network with backpropagation did not improve the result; this implies that the filters we created are already good filters given the training set. Our feature extractor training method was able to learn good filters from a minimal set of images. VGG has many parameters to learn, so it is susceptible to overfitting with such a small training set. We do not use any technique to handle small data sets to train VGG because we intended to verify our approach viability, and these techniques could also be used with our method. In Figure \ref{fig:ex-classification} we can see examples of misclassified images. In these images, coconut trees appear in different angles, sizes, and shapes, or the boundaries between the coconut tree and the background are tenuous, making it more difficult to identify them. In turn, images that do not contain coconut trees, contain trees that resemble their shape. The nete
